\textbf{Adaptation of the PHQ-4 Short Screening for Depression and Anxiety to increase its Sensitivity to Subclinical Variability}

### 2023-01-09 paper/manuscript.Rmd
update

Future studies should further corroborate our statistical validation and test the usefulness of this revision on more targeted samples (e.g., clinical populations), cross-validate it with other more comprehensive measures, and refine the normalized scoring estimates in larger sample.

@@

```{r message=FALSE, warning=FALSE}
# Load the function
source()
```

>>>>

The added value in terms of finer sensitivity that we hypothesize should be confirmed by cross-validating the PHQ-4R with more comprehensive measures of anxiety and depression. Additionally, evidence comparing the refined version against the original PHQ-4 would be useful to better understand whether the new "Once or twice" option pulls participants that would have otherwise answer "Not at all" or "Several days". Finally, future studies should further corroborate our statistical validation and test the usefulness of this revision on more targeted samples (e.g., clinical populations) to see if it affects the cut-offs proposed in the literature (and whether it allows for a better discrimination of mood disorders), and refine if need be the normalized scoring estimates in larger sample.

@@

```{r message=FALSE, warning=FALSE}
# Load the function
source("https://raw.githubusercontent.com/DominiqueMakowski/PHQ4R/main/score_PHQ4.R")

score_PHQ4(A1 = "Not at all", A2 = "Once or twice",
           D1 = "Once or twice", D2 = "several days",
           method = "basic")
```
